Be assured  that the essence  of piety toward the  gods lies in  this---to form
right  opinions concerning  them, as  existing  and as  governing the  universe
justly and well. And  fix yourself in this resolution, to  obey them, and yield
to them,  and willingly follow  them amidst all events,  as being ruled  by the
most perfect  wisdom. For  thus you will  never find fault  with the  gods, nor
accuse them of neglecting  you. And it is not possible for  this to be affected
in any other way than by withdrawing  yourself from things which are not within
our own power, and  by making good or evil to consist only  in those which are.
For if you suppose any other things to be either good or evil, it is inevitable
that, when you are disappointed of what you wish or incur what you would avoid,
you should  reproach and blame their  authors. For every creature  is naturally
formed to flee and abhor things that appear hurtful and that which causes them;
and to  pursue and admire those  which appear beneficial and  that which causes
them.  It is  impracticable, then,  that one  who supposes  himself to  be hurt
should  rejoice in  the person  who, as  he thinks,  hurts him,  just as  it is
impossible to rejoice in  the hurt itself. Hence, also, a  father is reviled by
his son when he does not impart the things which seem to be good; and this made
Polynices and Eteocles\footnotemark mutually  enemies---that empire seemed good
to both.  On this  account the  husbandman reviles  the gods;  [and so  do] the
sailor, the  merchant, or  those who  have lost  wife or  child. For  where our
interest  is, there,  too, is  piety directed.  So that  whoever is  careful to
regulate his desires  and aversions as he  ought is thus made  careful of piety
likewise. But  it also  becomes incumbent  on everyone  to offer  libations and
sacrifices and first  fruits, according to the customs of  his country, purely,
and not  heedlessly nor negligently;  not avariciously, nor  yet extravagantly.
\footnotetext{The  two inimical  sons  of  Oedipus, who  killed  each other  in
battle.---Ed.}
