Whatever moral rules you have deliberately  proposed to yourself. abide by them
as they were laws, and as if you would be guilty of impiety by violating any of
them. Don't regard what anyone says of  you, for this, after all, is no concern
of yours.  How long,  then, will you  put off thinking  yourself worthy  of the
highest improvements and  follow the distinctions of reason?  You have received
the philosophical theorems,  with which you ought to be  familiar, and you have
been familiar  with them. What  other master, then, do  you wait for,  to throw
upon that the delay of reforming yourself? You are no longer a boy, but a grown
man.  If,  therefore, you  will  be  negligent  and  slothful, and  always  add
procrastination to procrastination,  purpose to purpose, and fix  day after day
in which  you will  attend to  yourself, you  will insensibly  continue without
proficiency, and, living and dying, persevere  in being one of the vulgar. This
instant,  then, think  yourself worthy  of  living as  a  man grown  up, and  a
proficient. Let whatever  appears to be the  best be to you  an inviolable law.
And if any  instance of pain or  pleasure, or glory or disgrace,  is set before
you, remember that now is the combat, now  the Olympiad comes on, nor can it be
put off.  By once  being defeated and  giving way, proficiency  is lost,  or by
the  contrary preserved.  Thus Socrates  became perfect,  improving himself  by
everything,  attending to  nothing but  reason. And  though you  are not  yet a
Socrates, you ought, however, to live as one desirous of becoming a Socrates.
