Never afflict yourself with such reflections  as I shall live without honor and
never be anybody anywhere. For if to live without honor be really a misfortune,
know that  it is not possible  for you to  fall into misfortune, any  more than
into vice, through anything  that another can do. Is it then  of your own doing
that you are appointed to the magistracy or invited to feasts? By no means. How
then is this  to be without honor? And  how do you say that you  shall never be
anybody, whose part it is to be somebody in those things only which depend upon
yourself, and in which it is in your power to be of the highest worth?

\emph{But  then I  can be  of no  service to  my friends?}  How say  you of  no
service? Certainly they shall not have money  from you, nor will you be able to
get them made Roman citizens. But who  told you that these things were of those
that depend upon ourselves,  and were not alien to us? And who  is able to give
that which be himself has not?

Acquire then,  they say, in order  that we may possess,  Well, if I am  able to
acquire, without a  loss of modesty, or faith, or  high-mindedness, show me the
way, and I  will do it. But if  you require me to sacrifice that  which I have,
which is  really good, in order  that you may compass  what is no good  at all,
behold how unjust and  inconsiderate you are! And is it  not better than money,
to have faith and modesty in a friend?  Then rather help me on my way, and take
part with me, than require me to  do anything which would compel me to renounce
these things.

But,  you say,  \emph{I shall  not be  bearing  my part  in the  service of  my
country!} Again, what do you take service  to consist in? Your country will not
be enriched  through you  with porticos  and public baths.  And what  then? The
smith does not supply her with shoes, nor the shoemaker with weapons, but it is
enough that every  man fulfil his own  work, And if you have  made one faithful
and modest citizen for her, are you then of no service? Wherefore neither shall
you be useless to your country.

\emph{What place then, you say, shall I  hold in the State?} Whatever place you
are able to hold,  guarding still your modesty and faith. But  if you cast away
these things  in order to be  of service to the  State, of what service  do you
think  you  will be  to  her  then, when  you  are  perfected in  the  contrary
qualities?
